---
title: "Index"
---
## About Me

Hi, my name is Mahisa Alam. I am a graduate student at Baruch College and I am pursuing my masters in Business Analytics with a concentration in Marketing Analytics. 

I pursed Digital Marketing during as an undergrad and decided to further my degree into Marketing Analytics to connect my creative side with data and be an essential asset to businesses, as I can be able to provide efficient insights while creating campaigns so that they can succeed. 

Outside of school, my hobbies consists of illustrating and Pilates.

This website will contain my projects for STA 9750.

[LinkedIn](www.linkedin.com/in/mahisa-alam)

```{r}
#| include: false
1+1
```

--------------

Last Updated: `r format(Sys.time(), "%A %m %d, %Y at %H:%M%p")`

--------------
```{r}
#| echo: false
#| message: false
#| warning: false

if(!require("leaflet")){
    options(repos=c(CRAN="https://cloud.r-project.org"))
    install.packages("leaflet")
    stopifnot(require("leaflet"))
}

baruch_longitude <- -73.98333
baruch_latitude  <- +40.74028

leaflet() |>
  addTiles() |>
  setView(baruch_longitude, baruch_latitude, zoom=17) |>
  addPopups(baruch_longitude, baruch_latitude, 
            "I am a Master's student at <b>Baruch College</b>!")
```
