---
title: "Index"
---
## About Me

Hi, my name is Mahisa Alam. I am a graduate student at Baruch College and I am currently pursuing my Masters in Business Analytics with a concentration in Marketing Analytics. 

I pursued a Bachelors Degree in Digital Marketing as an undergrad and decided to further my degree into Marketing Analytics to connect my creative side with data so I can be an essential asset to businesses, providing efficient insights and creating campaigns. 

Outside of school, my hobbies consists of illustrating and Pilates.

This website will contain my projects for STA 9750.

[LinkedIn](https://www.linkedin.com/in/mahisa-alam)

```{r}
#| include: false
1+1
```

--------------

Last Updated: `r format(Sys.time(), "%A %m %d, %Y at %H:%M%p")`

--------------
```{r}
#| echo: false
#| message: false
#| warning: false

if(!require("leaflet")){
    options(repos=c(CRAN="https://cloud.r-project.org"))
    install.packages("leaflet")
    stopifnot(require("leaflet"))
}

baruch_longitude <- -73.98333
baruch_latitude  <- +40.74028

leaflet() |>
  addTiles() |>
  setView(baruch_longitude, baruch_latitude, zoom=17) |>
  addPopups(baruch_longitude, baruch_latitude, 
            "I am a Master's student at <b>Baruch College</b>!")
```
